%!TEX TS-program = xelatex

\documentclass[a4paper,online]{adcv}
\usepackage[english]{babel}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[export]{adjustbox}
\usepackage[nodayofweek]{datetime}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=E07A5F,
    filecolor=E07A5F,      
    urlcolor=E07A5F,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }


\title{Titouan Renard's CV}

\addbibresource{bib_titouan_renard.bib}
\adcvname{Titouan}{Renard}{}
\adcvtitle{Political Economy Student}
\adcvaddress{}{}{Rue de la Paix 9, 1020 Renens}{Switzerland}
\adcvemail{titouan.renard}{etu.unige}{ch}
\adcvphone{(+41) 79 944 61 65}
\adcvwebsite{https://github.com/renarddesneiges/}{github account}
\adcvdate{October 2025}

\begin{document}

Political economy student with a background in robotics and artificial intelligence, I 
have strong foundations in mathematics, strong abstract reasoning skills, and extensive
programming experience. Before political economy, I was mostly interested in optimal 
control, reinforcement learning and learning theory. Now I am mostly interested in 
%heterodox 
international economics, crises and complexity economics.

\section{Education}

\begin{adcvtabletwo}
  \adcvrowtwo{\textbf{Master in Political Economy of Capitalism}, Geneva, Switzerland}{2024-Present}
  \adcvrowmulti{UNIGE}
  \adcvrowtwo{\textbf{Master in Robotics with a Minor in Data Science}, Lausanne, Switzerland}{2023}
  \adcvrowmulti{EPFL, STI and IC faculties}
  %\adcvrowskip
  \adcvrowtwo{\textbf{Bachelor in Microengineering}, Lausanne, Switzerland}{2020}
  \adcvrowmulti{EPFL, STI faculty}
  %\adcvrowskip
  \adcvrowtwo{\textbf{Bilingual Maturité}, Neuchâtel, Switzerland}{2016}
  \adcvrowmulti{French-English bilingual high-school, Lycée Denis de Rougemont, Major in Physics and Applied Mathematics}
\end{adcvtabletwo}

\section{Past Projects}

\begin{adcvtabletwo}
  \adcvrowtwo{\textbf{Swiss Financial Diplomacy in the Interwar Period, Preserving Bondholders' Interests in the Context of the Renegotiation of the Ottoman Public Debt (1919-1928)}, seminar paper for the course ``History of Financial Crises'' at UNIGE, under ther supervision of Prof. Juan Flores Zendejas. Project Graded \textit{6/6}}{2025}
  \adcvrowmulti{Investigated the collaboration between Swiss Diplomats and Bondholders using diplomatic archival sources.}
  \adcvrowtwo{\textbf{Provable Convergence Guarantees for Constrained Inverse Reinforcement Learning}, master project at SYCAMORE (Systems Control and Multiagent Optimization Research) at EPFL, under ther supervision of Prof. Maryam Kamgarmour. Project Graded \textit{6/6}}{2023}
  \adcvrowmulti{Proved convergence guarantees for a constrained IRL algorithm.}
  \adcvrowtwo{\textbf{Learning Motor Policies with Time Continuous Neural Networks}, semester project supervised by two labs, BIOROB (Biorobotics) and LCN (Laboratory of Computational Neuroscience) at EPFL, under ther supervision of Prof. Auke Ijspeert and Prof. Wulfram Gerstner. Project Graded \textit{6/6}}{2022}
  \adcvrowmulti{Work on the use of time continuous neural networks (Liquid Time-Constant Neural Networks) to solve control problems using reinforcement learning methods.}
  %\adcvrowskip
  \adcvrowtwo{\textbf{Power-Optimal Trajectory Generation for Airborne Wind Energy}, semester project at LA3 (EPFL), under ther supervision of Prof. Colin Jones. Project graded \textit{6/6}.}{2021}
  \adcvrowmulti{Worked on a strongly non-linear and non-convex optimization problem, implemented an appropriate iterative solver method to deal with the non-convexity in Matlab.}
  %\adcvrowskip
  \adcvrowtwo{\textbf{Deep Robust Navigation with Cognitive Mapping Visual Representations}, project done in the "Visual Intelligence - Machines and Minds" course at (EPFL), supervised by Prof. Amir Zamir. Project graded \textit{5.75/6}.}{2021}
  \adcvrowmulti{Development and implementation of a novel deep-reinfocement learning method for visual navigation.  \href{https://youtu.be/lYVNoB75AK4}{Presentation Video of the Project.}}

  %\adcvrowskip
\end{adcvtabletwo}  


\section{Experience}

\begin{adcvtabletwo}
  \adcvrowtwo{\textbf{Internships}}{} 
  \adcvrowtwo{\textit{Research Intern} at SYCAMORE (Systems Control and Multiagent Optimization Research) at EPFL, under the supervision of Maryam Kamgarmour}{2023}
  \adcvrowmulti{Worked on the sample complexity of Inverse Reinfocement Learning (upcoming publication).}
  \adcvrowtwo{\textit{Course Project Design} at the Laboratory of Computational Neuroscience, under the supervision of Alireza Modirshanechi}{2023}
  \adcvrowmulti{Designed the course project for the Artifical Neural Networks and Reinfocement Learning course at EPFL.}
  \adcvrowtwo{\textit{Machine-Learning Intern} at 3HLE Robotics and Automation}{2022-2023}
  \adcvrowmulti{Worked on deep-learning models for \textit{6D pose estimation} from rgbd sensor data in the context of industrial robotics maniplation, under the supervision of Laurent Winkler}
  %\adcvrowskip
  %\adcvrowskip
  \adcvrowtwo{\textit{Summer Internship}, at EPFL's Birorobotics Lab, under the supervision of Alessandro Crespi.}{2018}
  \adcvrowmulti{Implementation of a simple vision-based localization system using C++ and OpenCV.}
  \adcvrowtwo{\textbf{Student-Assistant at EPFL}}{} 
  \adcvrowtwo{\textit{Artifical Neural Networks and Reinfocement Learning}}{2022-2023}
  \adcvrowmulti{For the Computer Science and Data Science students.}
  %\adcvrowskip
  \adcvrowtwo{\textit{"Physique Générale 1"} (Newtonian Mechanics)}{2018-2021}
  \adcvrowmulti{For the PH-101(b) (Microengineering, Electrical Engineering and Material Sciences sections) and PH-101(d) courses (for the Mechanical Engineering section).}
  %\adcvrowskip
  \adcvrowtwo{\textit{"Microinformatique"} (basics of embedded systems programming)}{2019}
  \adcvrowmulti{For the Microengineering students.}
  % \adcvrowskip
  \adcvrowtwo{\textit{Basics of Robotics}}{2018}
  \adcvrowmulti{For the Microengineering students.}
  %\adcvrowskipà
  \adcvrowtwo{\textit{Material Sciences Practicals}}{2018}
  \adcvrowmulti{For the Microengineering and Material sciences students.}
  %\adcvrowskip
  \adcvrowtwo{\textbf{Other}}{} 
  \adcvrowtwo{\textit{Webmaster} for Institut de Psychanalyse Charles Baudouin}{2025-present}
  \adcvrowmulti{Development, maintenance and updating of the institute's website. }
  % \adcvrowtwo{\textit{Graphic Design Freelance Work} for EPFL's VPT (Vice-présidence pour la transformation responsable)}{2022}
  % \adcvrowmulti{Designed an event-related newspaper.}
\end{adcvtabletwo}  

\section{Skills}

\begin{adcvtabletwo}
  \adcvrowtwo{\textbf{Programming}, in C, C++, Javascript, Matlab, Python and Scala.}
  \adcvrowskip
  \adcvrowtwo{\textbf{Math and Applied Math}, Probabilities, Linear Algebra, Calculus, Dynamical Systems and Control Theory, Algorithmic Design and Analysis, Econometrics. Strong abstraction capacity, ability to mathematically formulate a concrete problem.}
  \adcvrowskip
  \adcvrowtwo{\textbf{Soft Skills}, public speaking, writing and team management learned in the context student associations, graphic design, French (native proficiency), English (full proficiency), German (B2)}{}
\end{adcvtabletwo}  



% \section{Relevant Courses}

% \begin{adcvtabletwo}
%   \adcvrowtwo{\textbf{Course}}{\textbf{Grade}}
%   \adcvrowtwo{Networks out of Control (COM-512)}{5.25/6}
%   \adcvrowtwo{Visual Intelligence, Machines and Minds (CS-503)}{5.75/6}
%   \adcvrowtwo{Legged Robotics (MICRO-507)}{5.75/6}
%   \adcvrowtwo{Model Predictive Control (ME-425)}{5.75/6}
%   \adcvrowtwo{Algorithms (CS-250)}{5.5/6}
%   \adcvrowtwo{Advanced Algorithms (CS-450)}{6/6}
%   \adcvrowtwo{Artifical Neural Networks (CS-456)}{5.75/6}
%   \adcvrowtwo{Aerial Robotics (MICRO-502)}{5/6}
%   \adcvrowtwo{Computer Vision (CS-442)}{5.5/6}
%   \adcvrowtwo{Distributed Intelligent Systems (ENG-466)}{5/6}
%   \adcvrowtwo{Analysis and Modelling of Locomotion (BIOENG-404)}{5/6}
%   \adcvrowtwo{Functional Programming (CS-210)}{5.5/6}
% \end{adcvtabletwo}  

\section{Volunteer Experience}

\begin{adcvtabletwo}
  \adcvrowtwo{\textbf{Unipoly}, student's association for sustainabily at EPFL.}{2019-2022}
  %\adcvrowskip
  \adcvrowmulti{Board member, then president of an association of approximately 300 membres with a 20'000 CHF annual budget.}
  %\adcvrowskip
  % \adcvrowtwo{\textit{Président}}{2021-2022}
  % \adcvrowmulti{Experience with team management and budgets.}
  % %\adcvrowskip
  % \adcvrowtwo{\textit{Responsable Politique},}{2020-2021}
  % \adcvrowmulti{Experience in interactions with stakeholders and EPFL's direction on matters of sustainabily on campus.}
  % %\adcvrowskip
  % \adcvrowtwo{\textit{Responsible of Events} for the 2020 sustainabily week on EPFL campus}{2019-2020}
  % \adcvrowmulti{Management and coordination of about 30 events (conferences, workshops) on EPFL and UNIL's campuses.}
  % %\adcvrowskip
  % \adcvrowtwo{\textit{Writer} for Unipoly's Journal}{2019-2021}
  % \adcvrowmulti{One to two articles per year.}
  %\adcvrowskip
  \adcvrowtwo{\textbf{European Youth Parliament}, Switzerland}{2015-2016} 
  \adcvrowmulti{English language public speaking experience.}
\end{adcvtabletwo}  


\section{Publications}

  % \begin{refsection}
  %   \nocite{renardEcoloLuttesSociales2019}
  %   \nocite{renardBusinessAsUsual_1_2020}
  %   \nocite{renardBusinessAsUsual_2_2020}
  %   \nocite{renardBusinessAsUsual_3_2020}
  %   \nocite{renardSiLEcologie2020}
  %   \nocite{renardCollapso}
  %   \nocite{renardCampusExpress}
  %   \nocite{renardVPOP}
  %   \printbibliography[title={Newspaper articles}, heading=subbibliography]
  % \end{refsection}
  \begin{refsection}
    \nocite{morgan2025}
    \nocite{renardMaster}
    \nocite{renardIRL}
    \nocite{tumultePostCorona2020}
    \nocite{desobeirPourLaTerre2021}
    \printbibliography
  \end{refsection}
  % \begin{refsection}
  %   \printbibliography[title={Contribution to books}, heading=subbibliography]
  % \end{refsection}


\end{document}
